Manuscript title here

### 2024-09-22 manuscript.Rmd
2 version för determine vilken class

To classify the patients the following measurement will be used as independent variables for classification of shock regardless of their cause. Heart rate(HR), blood pressure(BP), respiratory rate(RR) and mental status. Based on these four measurements, the patients will be classified into four groups roughly based on the same value as in the ATLS trauma shock classifications.

@@

Version 1,
Due to the newer versions of ATLS classifications lack actual numbers, we will be using simplified and numerical version approximated by Dunham et al[@dunham_comparison_2017].

Version 2,
Due to the newer versions of ATLS classifications lack actual numbers, we will be approximating the values to numbers. For HF... For BP

The first group will be patients presenting with a HR below 100 beats per minute(BPM), respiratory rate between 14 to 20. The original ATLS classification only states normal BP, but no number. In our case, we will be using the systolic over 90mmhg as the lower limit up to 65 years old, and 110mmhg as the lower limit for patients older (geriatric patients). The...

>>>>

To classify the patients the following measurement will be used as independent variables for classification of shock regardless of their cause. Heart rate(HR), systolic blood pressure(SBP), respiratory rate(RR) and mental status. Based on these four measurements, the patients will be classified into four groups roughly based on the same value as in the ATLS trauma shock classifications.

@@

Version 1,
Due to the tenth edition of ATLS classifications lack actual numbers, we will be using simplified and numerical version approximated by Dunham et al[@dunham_comparison_2017]. (INSERT PICTURE)

Version 2,
Due to the tenth edition of ATLS classifications lack actual numbers, we will be approximating numbers to the values. For HR and RR we will be using the numbers from the ninth edition of the classification. The SBP will be divded into class I and II where the SBP is >110, class III 110-90mmhg and class IV <90mmhg. This selection is based on tenth edition, where SBP is defined as normal i class I to II and normal/below in class III and clearly below normal i class IV. These two studies, defined hypotension as 110mmhg respective 90mmhg dependent on age, therefore we choose class III as 110-90mmgh and class IV below 90mmhg. For mental status, according to the tenth edition ATLS, class I and II should have normal GCS, and class III and IV have lower GCS. Therefore we decided to use GCS 15 for class I + II and GCS <15 for class III and IV.
